DATA 624 Homework 6

### 2020-03-19 DATA624/HW6.Rmd
More work on HW6

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

**In order to see the effects of a change in $ϕ_1$ we will need to modify the code a little bit:**

```{r}
sim_AR1 <- function(phi){
  set.seed(42)
  y <- ts(numeric(100))
  e <- rnorm(100)
  for(i in 2:100){
    y[i] <- phi*y[i-1] + e[i]
  }
  return(y)
}

p <- autoplot(sim_AR1(0.6))
for(phi in seq(0.1, 0.9, 0.1)){
  p <- p + autolayer(sim_AR1(phi), series = paste(phi))
}
p +
  labs(title="The effects of changing Phi", color = "Phi") +
  theme(axis.title = element_blank(), legend.position = "bottom") +
  scale_color_brewer(palette = "Set1")
```

**Now with a fixed random number seed we can see the effect.  As $ϕ_1$ increases, the distance from zero increases.  It increases the autocorrelation with the preceeding value.**

@@

```{r}
sim_MA1 <- function(theta){
  set.seed(42)
  y <- ts(numeric(100))
  e <- rnorm(100)
  e[1] <- 0
  for(i in 2:100){
    y[i] <- theta*e[i-1] + e[i]
  }
  return(y)
}
```

@@

```{r}
p <- autoplot(sim_MA1(0.6))
for(theta in seq(0.1, 0.9, 0.1)){
  p <- p + autolayer(sim_MA1(theta), series = paste(theta))
}

p +
  labs(title="The effects of changing Theta", color = "Theta") +
  theme(axis.title = element_blank(), legend.position = "bottom") +
  scale_color_brewer(palette = "Set1")
```

**This is a bit harder to see but as $ϕ_1$ increases, the distance from zero again increases.  The $θ_1$ deals with the error so it is not as pronounced as a change in $ϕ_1$ though.**

@@

```{r}
sim_ARMA <- function(phi, theta){
  set.seed(42)
  y <- ts(numeric(100))
  e <- rnorm(100)
  e[1] <- 0
  for(i in 2:100)
    y[i] <- phi*y[i-1] + theta*e[i-1] + e[i]
  return(y)
}
```

@@

```{r}
sim_AR2 <- function(phi_1, phi_2){
  set.seed(42)
  y <- ts(numeric(100))
  e <- rnorm(100)
  for(i in 3:100)
    y[i] <- phi_1*y[i-1] + phi_2*y[i-2] + e[i]
  return(y)
}
```

@@

```{r}
autoplot(sim_ARMA(0.6, 0.6), series = "ARMA(1,1)") +
  autolayer(sim_AR2(-0.8, 0.3), series = "AR(2)") +
  theme(axis.title = element_blank(), legend.position = "bottom", legend.title = element_blank()) +
  scale_color_brewer(palette = "Set1")
```

@@

```{r}
autoplot(wmurders) +
  ggtitle("Women Murdered in the U.S.") +
  theme(axis.title = element_blank())
```

**The trends (both up and down) suggest that the series should be differenced before moving forward.  `ndiffs` estimates that `r ndiffs(wmurders)` differened are required to make this time series stationary.**

```{r}
ggtsplot(diff(wmurders, ndiffs(wmurders)), "Differenced Women Murdered in the U.S.")
```

**The first lag of the PACF is the only spike which indicates the value of p in the ARIMA model should be 1.  The high first value in the ACF indicates that the p is also one.**

@@

**No.  Because the differencing term (d) is 2.  We should not include it in the model.**

@@

```{r}
auto.arima(wmurders)
```
